Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeast Taiwan

### 2019-10-29 analysis/paper/paper.Rmd
update code

```{r read-data}
library(here)
lf <- list.files(here("analysis", "data", "raw_data"), full.names = TRUE)

@@

  write_xml(t1,
            str_glue("analysis/data/raw_data/fill_{basename(svg_file)}"))

  # fit image object to canvas in svg so it's all captured during the conversion to JPG
  system(str_glue('inkscape --verb=EditSelectAll --verb=AlignHorizontalCenter --verb=AlignVerticalCenter  --verb=FitCanvasToSelectionOrDrawing --verb=FileSave --verb=FileQuit "$(pwd)/analysis/data/raw_data/fill_{basename(svg_file)}"'))
}

@@

# convert SVG to PNG
filled_svgs <- list.files("analysis/data/raw_data", pattern = "^fill_", full.names = TRUE)

@@

# get list of jpgs only
jpgs <- list.files("analysis/data/raw_data", pattern = ".jpg", full.names = TRUE)

# join file names to phase
pottery_data <- readr::read_csv("Pottery_outlines/KWL_Ceramic_final2018_with_phases.csv")
pottery_data <- pottery_data %>% 
  mutate(filename = str_glue('fill_{filename}.svg_output.jpg'))

@@

pile(jpgs_imported_coo)

>>>>

```{r read-data}
library(here)
lf <- list.files(here("analysis", "data", "raw_data", "pottery_svg"), full.names = TRUE)

@@

  write_xml(t1,
            str_glue("analysis/data/raw_data/fill_pottery_svg/fill_{basename(svg_file)}"))

  # fit image object to canvas in svg so it's all captured during the conversion to JPG
  system(str_glue('inkscape --verb=EditSelectAll --verb=AlignHorizontalCenter --verb=AlignVerticalCenter  --verb=FitCanvasToSelectionOrDrawing --verb=FileSave --verb=FileQuit "$(pwd)/analysis/data/raw_data/fill_pottery_svg/fill_{basename(svg_file)}"'))
}

@@

# convert SVG to PNG
filled_svgs <- list.files("analysis/data/raw_data/fill_pottery_svg", pattern = "^fill_", full.names = TRUE)

@@

# get list of jpgs only
jpgs <- list.files("analysis/data/raw_data/pottery_jpg", pattern = ".jpg", full.names = TRUE)

# join file names to phase
pottery_data <- readr::read_csv("analysis/data/raw_data/KWL_Ceramic_final2018_with_phases.csv")
pottery_data <- pottery_data %>% 
  mutate(filename = str_glue('fill_{filename}.svg_output.jpg'))

@@

pile(jpgs_imported_coo)
```

```{r EFA-analysis}
op <- efourier(jpgs_imported_coo, norm = FALSE)

# The progressive capture of shape geometry along the number of harmonics can be visualized with:

calibrate_reconstructions_efourier(jpgs_imported_coo,  
                          id = 1, 
                          range = c(1, 2, 4, 8, 14, 20))

# mean shape, per group
bot.ms <- mshapes(op, 2)
bot.ms$shp$`Post-European`   <- bot.ms$shp$`Post-European` %T>% coo_plot(border="blue")
`Post-European`  <- bot.ms$shp$`Post-European`  %T>% coo_draw(border="blue")
`Pre-European` <-   bot.ms$shp$`Pre-European`  %T>% coo_draw(border="red")
legend("topright", 
       lwd=1,
       col=c("blue", "red"), 
       legend=c( "Post-European", "Pre-European"))

# Thin plate spline analysis (TPS)
# Thin plate splines (TPS) was used to compare average shapes and visualise the outline deformations required to pass from an extreme of the morphospace to the other.
# Deformation grids
png("Pottery_outlines/tps-pre-Euro-to-post-Euro.png", res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Post-European` , shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

png("Pottery_outlines/tps-pre-Euro-to-Chinese.png", res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Chinese Contact`, shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

# Isodeformation lines
tps_iso(`Pre-European`, `Post-European`,  shp.lwd = c(2, 2), shp.border = c("red", "blue"),
        amp = 0.5, iso.nb = 10000, iso.levels = 12, legend.text = c("Pre-contact", "Post-contact"),
        palette = col_summer, grid = F)
